---
title: "Plotly"
author: "Yanyuan Zhu"
date: "9/7/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```
## Introduction
- Create a web page presentation using R Markdown that features a plot created with Plotly. 
- Host your webpage on either GitHub Pages, RPubs, or NeoCities. 
- Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

## Introduction

- The URL presentation of R Markdown is

<a href="https://github.com/caoanroad4800/datasciencecoursera/blob/master/09_Developing_Data_Products/Peer-graded_Assignment_R_Markdown_Leaflet.Rmd">https://github.com/caoanroad4800/datasciencecoursera/blob/master/09_Developing_Data_Products/Peer-graded_Assignment_R_Markdown_Leaflet.Rmd</a>

- The generated html URL is

<a href="https://caoanroad4800.github.io/datasciencecoursera/Peer-graded_Assignment_R_Markdown_Presentation_Plotly.html">https://caoanroad4800.github.io/datasciencecoursera/Peer-graded_Assignment_R_Markdown_Presentation_Plotly.html</a>


## Scatterplot Color
```{r, echo = FALSE, message=FALSE}
plot_ly(mtcars, x = mtcars$wt, y = mtcars$mpg, 
        mode = 'markers', color = as.factor(mtcars$cyl))
```


