---
title: "R Markdown Presentation"
author: "Yanyuan Zhu"
date: "9/6/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## My new slide

Plain text

*Italicized text*

**Bold text**

`for (i %in% 1:10)`

```{r, echo = TRUE, comment = ""}
head(mtcars)
```

## Load `mtcars` data
argument `{r, echo = TRUE, comment = ""}`

```{r, echo = TRUE, comment = ""}
head(mtcars)
```

## My new slide

```{r, echo = TRUE, fig.align='center', fig.cap="My awesome figure"}
plot(mtcars$wt, mtcars$mpg, main = "mtcars", xlab = "Weight"
     , ylab = "MPG", col = "red", pch = 2)
```


## Load `mtcars` data

argument `{r, eval = FALSE, comment = ""}`

```{r, eval=FALSE, comment = ""}
head(mtcars)
```


## My title 

### A top level subheading

#### A second level subheading

- Bullet 1
- Bullet 2

1. Item a
2. Item b

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

