---
title: "Peer-graded Assignment: Course Project 2"
author: "Yanyuan Zhu"
#output: html_document
output: md_document
---
## 1. Questions & Answers
- Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?
    - **Tornados have caused greated number of fatalities (5,633) and injuries (91,347)**
- Across the United States, which types of events have the greatest economic consequences?
    - **Floods have caused the most significant damage 144.7 Billion USD, followd by HURRICANE/TYPHOON with 69.3 Billion USD damage**

## 2. Data Processing
### 2.1 Environment

```{r echo = TRUE}
setwd("~/Soft/Rtest/datasciencecoursera/05_Reproducible_Research/")
library("data.table")
library("ggplot2")
```

### 2.2 Data download
```{r echo = TRUE}
# defile the url
#fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
# download the file into ./data/
#download.file(fileUrl, destfile = "./data/repdata_data_StormData.csv.bz2")
```

read the `csv.bz2` file, rename as `storm`
```{r echo = TRUE}
# load data frame
storm <- read.csv("./data/repdata_data_StormData.csv.bz2")
head(storm)
```

```{r echo = TRUE}
# shape of data frame
dim(storm) # 902297 x 37
```

```{r echo = TRUE}
str(storm)
```

```{r echo = TRUE}
# event types
length(unique(storm$EVTYPE)) # 985 event types
```

According to the [Storm Data Documentation](https://d396qusza40orc.cloudfront.net/repdata%2Fpeer2_doc%2Fpd01016005curr.pdf), the health variables include `FATALITIES` and `INJURIES`. with datamage to property `PROPDMG` and to crops `CROPDMG` We narrow down the column numbers to accelerate following analytics

### 2.3 Data subset

```{r echo = TRUE}
colList <- c("EVTYPE"
             , "FATALITIES"
             , "INJURIES"
             , "PROPDMG"
             , "PROPDMGEXP"
             , "CROPDMG"
             , "CROPDMGEXP"
)
storm <- storm[, colList]
head(storm)
```

There is 1 observation with `ENVTYPE == "?"` which should be removed as well
```{r echo = TRUE}
# sum(storm$EVTYPE=="?") # 1
# storm[(storm$EVTYPE=="?"), ] # may be due to measurement error
#storm <- 
storm <- storm[(storm$EVTYPE!="?"), ]
```

We see the following 4 columns have zero values (lucily there are no negative values), meaning it caused no harm to population health, and are also removed by rows

### 2.4 Missing values
```{r echo = TRUE}
summary(storm$INJURIES)
summary(storm$FATALITIES)
summary(storm$PROPDMG)
summary(storm$CROPDMG)
```

```{r echo = TRUE}
storm <- storm[(storm$INJURIES > 0 | storm$FATALITIES > 0 | storm$PROPDMG > 0 | storm$CROPDMG > 0),]
dim(storm) # (902297x37) --> (254632x7)
head(storm)
```


### 2.5 -EXP column conversions

Change PROPDMGEXP and CROPDMG columns into upper case

```{r echo = TRUE}
storm$PROPDMGEXP <- toupper(storm$PROPDMGEXP)
storm$CROPDMGEXP <- toupper(storm$CROPDMGEXP)
```
Check if they are all upper case now
```{r echo = TRUE}
unique(storm$PROPDMGEXP)
```

```{r echo = TRUE}
unique(storm$CROPDMGEXP)
```

Map property damage alphanumeric exponents to numeric values
```{r echo = TRUE}
propDmgKey <-  c("\"\"" = 10^0,
                 "-" = 10^0, 
                 "+" = 10^0,
                 "0" = 10^0,
                 "1" = 10^1,
                 "2" = 10^2,
                 "3" = 10^3,
                 "4" = 10^4,
                 "5" = 10^5,
                 "6" = 10^6,
                 "7" = 10^7,
                 "8" = 10^8,
                 "9" = 10^9,
                 "H" = 10^2,
                 "K" = 10^3,
                 "M" = 10^6,
                 "B" = 10^9)
storm$PROPDMGEXP <- propDmgKey[as.character(storm$PROPDMGEXP)]
storm[is.na(storm[,'PROPDMGEXP']),'PROPDMGEXP'] <- 10^0
```

Map crop damage alphanumeric exponents to numeric values
```{r echo = TRUE}
cropDmgKey <-  c("\"\"" = 10^0,
                "?" = 10^0, 
                "0" = 10^0,
                "K" = 10^3,
                "M" = 10^6,
                "B" = 10^9)
storm$CROPDMGEXP <- cropDmgKey[as.character(storm$CROPDMGEXP)]
storm[is.na(storm[,'CROPDMGEXP']),'CROPDMGEXP'] <- 10^0
```
### 2.6 Calculate economic cost for property and crop

```{r echo = TRUE}
## add 2 new columns in storm
## propCost = PROPDMG * PROPDMGEXP
## cropCost = CROPDMG * CROPDMGEXP
storm$propCost = storm$PROPDMG * storm$PROPDMGEXP
storm$cropCost = storm$CROPDMG * storm$CROPDMGEXP
head(storm)
```

Calculate cost by EVTYPE
```{r echo = TRUE}
storm <- as.data.table(storm)
storm <- storm[, .(EVTYPE
          , FATALITIES
          , INJURIES
          , PROPDMG
          , PROPDMGEXP
          , propCost = PROPDMG * PROPDMGEXP
          , cropCost = CROPDMG * CROPDMGEXP
         )]
```

```{r echo = TRUE}
#storm <- as.data.table(storm)
totalCostDT <- storm[, .(propCost = sum(propCost)
                     , cropCost = sum(cropCost)
                     , totalCost = sum(propCost) + sum(cropCost)
                     ), by = .(EVTYPE)]
totalCostDT <- totalCostDT[order(-totalCost),]
totalCostDT <- totalCostDT[1:10, ]
head(totalCostDT)
```

###  2.7 Calculate total fatalities and injuries
```{r echo = TRUE}
totalFatalitiesDT <- storm[, .(FATALITIES = sum(FATALITIES)
                             , INJURIES = sum(INJURIES)
                             , totalS = sum(FATALITIES) + sum(INJURIES))
                          , by = .(EVTYPE)]
totalFatalitiesDT <- totalFatalitiesDT[order(-FATALITIES)]
totalFatalitiesDT <- totalFatalitiesDT[1:10,]
head(totalFatalitiesDT)
```

```{r echo = TRUE}
totalFatalitiesDT[EVTYPE == "TORNADO",]
```

## 3. Answers
### 3.1 Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?
```{r echo = TRUE}
#?melt
harmful_events <- melt(
    totalFatalitiesDT
    , id.vars = 'EVTYPE'
    , variable.name = "harm"
)
head(harmful_events)
```

```{r echo = TRUE}
str(harmful_events)
```

```{r echo = TRUE}
str(harmful_events$harm)
```

```{r echo = TRUE}
g <- ggplot(data = harmful_events
           , aes(x = reorder(EVTYPE, -value)
                , y = value)
           )
g <- g + geom_bar(
    color = "black"
    , stat = 'identity'
    , fill = "steelblue"
    , position = 'dodge'
)
g <- g + xlab("Event type") + ylab("Frequency count")
g <- g + ggtitle("Total Number of fatalities, 1950 - 2011")
g <- g + theme(axis.text.x = element_text(angle = 90, hjust = 1))
g
```

### 3.2 Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

```{r echo = TRUE}
econ_consequences <- melt(totalCostDT, id.vars = 'EVTYPE', variable.name = "Damage_Type")
head(econ_consequences)
```


```{r echo = TRUE}
g <- NULL
g <- ggplot(data = econ_consequences, aes(x = reorder(EVTYPE, -value), y = value))
g <- g + geom_bar(stat = 'identity', fill = 'red', position = "dodge")
g <- g + xlab("Event type") + ylab("Total damage (USD)")
g <- g + ggtitle("Total economic damage, 1950-2011, USD")
g <- g + theme(axis.text.x = element_text(angle = 90, hjust = 1))
g
```
