---
title: "Regression_Models_Course_Project"
author: "Yanyuan Zhu"
date: "Aug 28, 2020"
output:
  pdf_document: default
  html_document: default
---
### Question
You work for *Motor Trend*, a magazine about the automobile industry. Looking at a data set of a collection of cars, they are interested in exploring the relationship between a set of variables and miles per gallon (MPG) (outcome). They are particularly interested in the following two questions:

- “Is an automatic or manual transmission better for MPG”
- "Quantify the MPG difference between automatic and manual transmissions"

### Quick answers
- An manual transmission better for MPG
- Weight and drive speed affect mpg
    - Weight increase leads to mpg decrease
        - With weight increase 1000 lbs, the mpg decease by about 4 for automatic cars, and about 6 for manual cars
    - Drive speed increase ledas to mpg increase
        - With speed increase 1 second per 1/4 mile, the mpg increase about 0.8 for automatic cars, and about 1.4 for manual cars

### Enviroment settings


```{r, echo = TRUE}
library(car)
data(mtcars)
head(mtcars)
```

And each column class is following

```{r, echo = TRUE}
str(mtcars)
```
### EDA

There are 10 variables that may effect dependent variable `mpg`,we first check the correlations

```{r, echo = TRUE}
cor(mtcars$mpg, mtcars[,-1])
```

So that for the 10 independent variables
- 5 may be positively related, including drat, qsec, vs, am, gear
- 5 may be negatively related, including cyl, disp, hp, wt, carb

### Which transmission is better for MPG

We need to change `am` class from numeric to factor

Besides, check column meanings using `?mtcars`, we see am=0 denotes automatic transmission, and am=1 for manual transmission

```{r, echo = TRUE}
mtcars$am = factor(mtcars$am)
levels(mtcars$am) <- c("Automatic", "Manual")
```

Conclusion: A box plot with transmission type in x axis and mpg in y axis shows that in genral, the **manual type autos drive more miles per gallon.**

```{r, echo = TRUE}
boxplot(mtcars$mpg ~ mtcars$am, data = mtcars, xlab="transmission type", ylab="miles per gallon", main = "mpg analysis by transmission type")
```

### MPG difference between automatic and manual transmissions - Quantify analysis

```{r, echo = TRUE}
fit <-  step(lm(mpg ~ . , data = mtcars), trace = 0, steps = 10000)
summary(fit)
```

So that we get 3 out of 10 independent variables of importance to mpg change: wt, qsec, and am, with $R^2 = 0.85$

Furthermore, we examine mpg ~ wt + qest correlation with am

```{r, echo = TRUE}
fit2 <- lm(mpg ~ am:wt + am:qsec, data = mtcars)
summary(fit2)
```

With total $R^2$ of 90%, all the coefficients are significant, and we have the following conclusions

- Weight increase leads to mpg decrease
    - With weight increase 1000 lbs, the mpg decease by about 4 for automatic cars, and about 6 for manual cars
- Drive speed increase ledas to mpg increase
    - With speed increase 1 second per 1/4 mile, the mpg increase about 0.8 for automatic cars, and about 1.4 for manual cars