---
title: "R Markdown Presentation"
author: "Yanyuan Zhu"
date: "9/6/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, eval = FALSE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles()
my_map = leaflet()
my_map = addTiles(my_map)
my_map
```

## Your First Map
```{r, echo = TRUE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles()
my_map
```

## Adding Markers
```{r, echo = TRUE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat = 31.240405, lng = 121.471495, popup = "Si Hang Cang Ku") %>%
  addTiles("test")
my_map
```

## Adding Many Markers
```{r, echo = TRUE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 31.2, max = 31.3)
                 , lng = runif(20, min = 121.4, max = 121.5))

df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers()
```

## Making Custom Markers
```{r echo = FALSE}
hopkinsIcon <- makeIcon(
  iconUrl = "http://brand.jhu.edu/content/uploads/2014/06/university.shield.small_.blue_.png",
  iconWidth = 31*215/230,
  iconHeight = 31,
  iconAnchorX = 31*215/230/2,
  iconAnchorY = 16
)

hopkinsLatLong <- data.frame(
  lat = c(39.2973166, 39.3288851, 39.2906617, 39.2970681, 39.2824806)
  , lng = c(-76.5929798, -76.6206598, -76.5469683, -76.6150537, -76.6016766)
)

hopkinsLatLong %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hopkinsIcon)
```

## Mapping Clusters
```{r, echo = TRUE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(500, min = 31.2, max = 31.3)
                 , lng = runif(500, min = 121.4, max = 121.5))

df %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```


## Mapping Circle Markers
Instead of adding markers or clusters you can easily add circle markers using 'addCircleMarkers()`
```{r, echo = TRUE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 31.2, max = 31.3)
                 , lng = runif(20, min = 121.4, max = 121.5))

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers()
```
## Drawing Circles
```{r, echo = FALSE}
md_cities <- data.frame(
  name = c("Baltimore", 
           "Frederick", 
           "Rockville", 
           "Gaithersburg", 
           "Bowie", 
           "Hagerstown", 
           "Annapolis", 
           "College Park",
           "Salisbury",
           "Laurel"),
  pop = c(619493, 66169, 62234, 61045, 55232,
          39890, 38880, 30587, 30484, 25346),
  lat = c(39.2920592, 39.4143921, 39.0840, 39.1434, 39.0068, 39.6418,
          39.9784, 38.9897, 38.3607, 39.0993),
  lng = c(-76.6077852, -77.4204875, -77.1528, -77.2014, -76.7791,
          -77.7200, -76.4922, -76.9378, -75.5994, -76.8483)
)

md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)
```


## Adding Legends

```{r, echo = TRUE}
set.seed(2016-04-25)
df <- data.frame(lat = runif(20, min = 31.2, max = 31.3)
                 , lng = runif(20, min = 121.4, max = 121.5)
                 , col = sample(c("red", "blue", "green"), 20, replace = TRUE)
                 , stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))
```

## Drawing Rectangles

```{r, eval=FALSE}
leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 37.3858, lng1 = -122.0595, 
                lat2 = 37.3890, lng2 = -122.0625)
```



## My new slide

Plain text

*Italicized text*

**Bold text**

`for (i %in% 1:10)`

```{r, echo = TRUE, comment = ""}
head(mtcars)
```

## Load `mtcars` data
argument `{r, echo = TRUE, comment = ""}`

```{r, echo = TRUE, comment = ""}
head(mtcars)
```

## My new slide

```{r, echo = TRUE, fig.align='center', fig.cap="My awesome figure"}
plot(mtcars$wt, mtcars$mpg, main = "mtcars", xlab = "Weight"
     , ylab = "MPG", col = "red", pch = 2)
```


## Load `mtcars` data

argument `{r, eval = FALSE, comment = ""}`

```{r, eval=FALSE, comment = ""}
head(mtcars)
```


## My title 

### A top level subheading

#### A second level subheading

- Bullet 1
- Bullet 2

1. Item a
2. Item b

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Your fist map

