---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Yanyuan Zhu"
date: "9/5/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

Diamond Data Analysis Report enabled developing data products using shiny apps being embeded within RMarkDown.

Using PageUp and PageDown keys all the slides can be traversed.

## Overview

- Links for the Application

**I failed to upload my shiny app into shinyapps.io due to the error, which happened when I tried to connect my Rstudio to shinyapps.io**
```{r echo=FALSE}
Error in dyn.load(file, DLLpath = DLLpath, ...) : 
  unable to load shared object '/home/yanyuan/R/x86_64-pc-linux-gnu-library/4.0/curl/libs/curl.so':
  /usr/lib/x86_64-linux-gnu/libcurl.so.4: version `CURL_OPENSSL_3' not found (required by /home/yanyuan/R/x86_64-pc-linux-gnu-library/4.0/curl/libs/curl.so)
```
The problem is: when i try to install libcur3, all R packages have to be remove.

- Links for compiled project files on GitHub

https://github.com/BenKarmay/Peer-graded-Assignment-Course-Project-Shiny-Application-and-Reproducible-Pitch

## Data

Dataset `diamons` from `ggplot2` package

```{r, echo=TRUE}
library("ggplot2")
dim(diamonds)
```

```{r, echo = TRUE}
head(diamonds)
```

